---
title: "Flight Analysis"
author: "Stacy Wilkerson"
output: 
  html_document:
    code_folding: hide
    keep_md: yes
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nycflights13)
library(mosaic)
library(pander)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(data.table)
```

## Background and Questions
You just started your internship at a big firm in New York, and your manager gave you an extensive file of flights that departed JFK, LGA, or EWR in 2013. From this data (install.packages(nycflights13)) your manager wants you to answer the following questions;

Question 1: If I am leaving before noon, what are my top two airline options at each airport (JFK, LGA, EWR) that will have the least amount of delay time?

Question 2: Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?

Question 3: Which destination airport is the worst airport for arrival time?

## Results

Question 1: 

JFK: Hawaiian Airiness and US Airlines

LGA: Frontier Airlines and Mesa Airlines

EWR: Virgin America and Alaska Airlines

Question 2: JFK

Question 3: EWR

## Analysis

### Question 1

```{r}
flights1 <- data.table(nycflights13::flights)
flights2 <- data.table(nycflights13::airlines)
flights3 <- merge(flights1, flights2, by = "carrier")
Q1flights <- filter(flights3, sched_dep_time < 1200)
Q1flights <- select(Q1flights, origin, carrier, name, dep_delay)
```



```{r, warning=FALSE}
ggplot(Q1flights, aes(x = name, y = dep_delay)) +
  geom_boxplot() +
  #geom_jitter(alpha = 0.6) +
  facet_grid(. ~ origin) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5))
```

For this graphic we are looking at departure delays based on airports and airlines. This graphic shows us the range of how long an airline was delayed for departure. If we look at the times when most of the flights got out on time of a little bit later then we can choose the top two airlines from each airport that we would recommend one take if they wanted to leave before noon. 

### Question 2

```{r}
Q2flights <- filter(flights3, carrier == "DL")
pander(favstats(Q2flights$arr_delay ~ Q2flights$origin))
```

This shows us the summary statistics of Delta Airlines based on the origin airports. This table shows us the five number summary which we can look at and see which origin airport is the best that minimizes chances of a late arrival time. 

### Question 3

```{r}
Q3flights <- select(flights3, dest, arr_delay, origin)
Q3flights1 <- group_by(Q3flights, dest)
Q3flights2 <- mutate(Q3flights1, arr_mean_delay = mean(arr_delay, na.rm = TRUE))
```

```{r message=FALSE, warning=FALSE}
ggplot(Q3flights2, aes(x = dest, y = arr_mean_delay)) +
  geom_point() +
  facet_grid(. ~ origin) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(hjust = 0.5))
```

This graphic shows us the average arrival delay time based on the airport and the airline. But it we just look at the airport then we can generally see which airport has the worst arrival times. 


