---
title: "Case Study 8: Interacting with time"
author: "Stacy Wilkerson"
output: 
  html_document:
    code_folding: hide
    keep_md: yes
    theme: cerulean  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(tidyverse)
library(forcats)
library(rio)
library(downloader)
library(readr)
library(riem)
library(lubridate)
library(magrittr)
library(tidyquant)
library(quantmod)
library(magrittr)
library(forcats)
library(RColorBrewer)
library(dygraphs)
library(timetk)
```

##Background 

Your data science income has ballooned, and you need to find somewhere to invest $25,000 that you have saved over the last year. You have a savvy investment friend that is kind enough to tell you ten stocks he has been watching during the last year. You will need to visualize the last five years performance to help in the in the conversation with your friend.

##Graphics

```{r message=FALSE, warning=FALSE, fig_width = 12}
tickers_today <- c("CXW", "F", "GM", "JCP", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT")
stockprices <-
  tq_get(tickers_today, get = "stock.prices", complete_cases = TRUE,
    from = "2012-10-01")
stocks <- stockprices %>%
  select(date, symbol, adjusted) %>%
  spread(key = symbol, value = adjusted) %>%
  tk_xts(.)
dygraph(stocks, main = "Stock Adjusted Based on Year", ylab = "Adjusted") %>%
  dyHighlight(highlightCircleSize = 5, 
      highlightSeriesBackgroundAlpha = 0.2,
      hideOnMouseOut = FALSE) %>%
     dyOptions(colors = brewer.pal(10, "Paired")[c(2, 5, 6, 8, 7, 4, 1, 10, 3, 9, 12)])
```

```{r message=FALSE, warning=FALSE}
adjusted <- stockprices %>%
  select(date, symbol, adjusted) %>%
  spread(key = symbol, value = adjusted) %>%
  tk_xts(.)
volume <- stockprices %>%
  select(date, symbol, volume) %>%
  spread(key = symbol, value = volume) %>%
  tk_xts(.)

#tickers_today <- c("CXW", "F", "GM", "JCP", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT")
#getSymbols(tickers_today)
#stock <- do.call(merge, lapply(tickers_today, function(x) Cl(get(x))))
dateWindow <- c("2012-10-01", "2013-10-01")

dygraph(volume, main = "Volume", group = "stock") %>%
  dyRangeSelector(dateWindow = dateWindow)

dygraph(adjusted, main = "Adjusted", group = "stock") %>%
  dyRangeSelector(dateWindow = dateWindow)
```

This graphics above looks at all of the stocks that our friend told us about. This is an interactive graphic that makes it easy to see how well or poorly these stocks were doing in the past years.

```{r}
stockprices %>%
  group_by(symbol) %>%
    ggplot(aes(x = date, y = adjusted)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
    labs(title = "Candlestick Chart", 
         y = "Closing Price", x = "") + 
  facet_wrap(~symbol) +
    theme_tq()
```

This candle stick graphic takes a deeper look into these stocks showing the increase and decline of these stocks over time. For analyzing stocks the candle stick graphic is a good one to use to show us what and when a stock is changing and by how how much. 

